Tennis doubles and ghosts

### 2025-12-03 inst/tennis.Rmd
more work on hyper3

```{r printH}
H3 <- as.hyper3(H)
H3

## 1&2 vs 3&4;  scoreline 9-2 (again), with lambda=1.2

f <- function(lambda){
  H3[c(p1=lambda,p2=lambda)] %<>% inc(9)
  H3[c(p3=1,p2=1)] %<>% dec(2)
  H3[c(p1=lambda,p2=lambda,p3=1,p2=1)] %<>% dec(11)
  return(H3)
}
f(1.1443345)
f(1.888888)
```

maximize:

```{r,maxH3,cache=TRUE}
tennis_H3_maxp <- maxp(H3)
tennis_H3_maxp
```

@@

```{r}
tennis_maxp
tennis_ghost_maxp
```

@@

```{r,label=saveghosttennisdataset}
save(tennis,tennis_maxp,tennis_ghost, tennis_ghost_maxp,file="tennis.rda")
```

>>>>

```{r defineadd12vs34}

## 1&2 vs 3&4;  scoreline 9-2 (again)
add12vs34 <- function(lambda){
    H3 <- hyper3()
    H3[c(p1=lambda,p2=lambda)] %<>% inc(9)
    H3[c(p3=1,p2=1)] %<>% inc(2)
    H3[c(p1=lambda,p2=lambda,p3=1,p2=1)] %<>% dec(11)
    return(H3 + as.hyper3(H))
}
```

```{r useadd12vs34, cache=TRUE}
add12vs34(1.88)
maxp(add12vs34(2.0), give=TRUE)$value
maxp(add12vs34(2.1), give=TRUE)$value
```

```{r defineprofilelikelihood12vs34}
L <- function(lambda){maxp(add12vs34(lambda), give=TRUE)$value}
```

```{r useprofilelikelihood12vs34, cache=TRUE}
lam <- exp(seq(from=log(0.9), to=log(60), len=20))
support <- sapply(lam, L)
```

```{r optimize12v34, cache=TRUE}
o <- optimize(L, interval=c(exp(1.5),exp(2.5)), maximum=TRUE)
o
lambda_max <- o$maximum
```

```{r plotproflike}
support <- support - max(support)
plot(log(lam), support,
     pch=16, type="b",
     xlab=expression(log(lambda)), ylab="log-Likelihood"
     )
abline(h=c(0,-2))
abline(v=c(0,log(lambda_max)), lty=2)
```

```{r maxtennis3, cache=TRUE}
tennis_hyper3_maxp <- maxp(add12vs34(lambda_max))
```

@@

```{r, showallmax}
tennis_maxp
tennis_ghost_maxp
tennis_hyper3_maxp
```

Visuals:

```{r plotallmax}
x1 <- tennis_maxp
x2 <- tennis_ghost_maxp[-1]
x2 <- x2/sum(x2)
x3 <- tennis_hyper3_maxp
x1
x2
x3
```

Above, observe how x2 and x3 are identical: evidently, in this case,
`hyper2` formalism is formally identical to `hyper3` formalism.
Visually:

```{r showall}
par(pty="s")
l <- c(0.15,0.3)
plot(x1, x2, asp=1, xlim=l, ylim=l, pch=16)
abline(0,1)
```

@@

```{r,label=saveghosttennisdataset}
save(tennis, tennis_maxp, tennis_ghost, tennis_ghost_maxp, file="tennis.rda")
```
